### 2017-09-26 Writing/draft.tex
Results part of the draft

@@@ NOTE: THESE RESULTS ARE NOT FINAL - I thus didn't spend too much time describing them @@@

\subsection{Effect of Character Differences on topology}
The overall amount of pairwise $CD$ in a matrix has an effect of the ability to recover the correct topology.
An overall decrease in $CD$ leads to an decrease in $NTS_{RF}$ (as a proxy for clade conservation - Fig. \ref{Fig:RF_results_best}) and in $NTS_{Tr}$ (as a proxy for taxa position - Fig. \ref{Fig:Tr_results_best}).
Conversely, an increase in $CD$ leads to an increase in in $NTS_{RF}$ (Fig. \ref{Fig:RF_results_best}) and $NTS_{Tr}$ (Fig. \ref{Fig:Tr_results_best}).
This beneficial effect can be contrasted however with a similar beneficial effect when simply randomising the character differences (Figs \ref{Fig:RF_results_best} and \ref{Fig:Tr_results_best}).

\subsubsection{Effect of the number of characters}
This negative effect of decreased $CD$ (and positive of increased $CD$) on topology is increased with the number of characters.
% Test pulled difference between character numbers.

\subsubsection{Effect of the number of taxa}
Conversely, the effect of variation in $CD$ doesn't seem to drastically increase with the number of taxa after 75 taxa in our simulations.
% Test pulled difference between number of taxa.

\subsection{Effect of Character Differences on the inference method}
There seems to be a strong effect on the ability to recover the correct topology depending on the tree inference method.
Parsimony trees seems to be more sensible than Bayesian ones.
% Test pulled difference between methods.

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Figures/RF_results_best.pdf} %TG: These figures will be cleaned up once I have the final results.
\caption{\small{Effect of Character Difference on recovering the ``best'' topology. The y axis represents the Normalised Tree Similarity using Robinson-Fould distance for matrices with 25, 75 and 150 taxa from top to bottom respectively. The x axis represents the different Character Difference scenarios and tree inference method with the Maximised Character Difference in Bayesian (red) and under Maximum Parsimony (orange), the Minimised Character Difference in Bayesian (dark green) and under Maximum Parsimony (light green) and the Randomised Character Difference in Bayesian (dark blue) and under Maximum Parsimony (light blue) for matrices of 100, 350 and 1000 characters in the panels from left to right.}}
\label{Fig:RF_results_best}
\end{figure}

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Figures/Tr_results_best.pdf} %TG: These figures will be cleaned up once I have the final results.
\caption{Effect of Character Difference on recovering the ``best'' topology. The axis are identical to figure \ref{Fig:RF_results_best} but y axis represents the Normalised Tree Similarity using Triplets distance.}
\label{Fig:Tr_results_best}
\end{figure}

% latex table generated in R 3.4.0 by xtable 1.8-2 package
% Fri Jul 28 10:29:26 2017
\begin{table}[ht]
\centering
\begin{tabular}{rlllrrrrrrrrr}
  \hline
Taxa & Char. & Method & \multicolumn{3}{c}{max \textit{vs}. min} & \multicolumn{3}{c}{max \textit{vs}. rand} & \multicolumn{3}{c}{min \textit{vs}. rand} \\
 & & & BC & W & p & BC & W & p & BC & W & p \\ 
  \hline
25 & 100 & Bay. & 0.67 & 1130.00 & \textbf{0.00} & 0.85 & 856.00 & \textbf{1.00} & 0.74 & 320.00 & \textbf{0.00} \\ 
   & 350 &   & 0.71 & 1236.50 & \textbf{0.00} & \textbf{0.96} & 844.00 & \textbf{1.00} & 0.73 & 338.00 & \textbf{0.00} \\ 
   & 1000 &   & 0.71 & 1321.50 & \textbf{0.00} & 0.89 & 802.00 & 1.00 & 0.67 & 226.00 & \textbf{0.00} \\ 
75 & 100 &   & 0.48 & 1366.50 & \textbf{0.00} & 0.66 & 1134.00 & \textbf{0.01} & 0.69 & 264.00 & \textbf{0.00} \\ 
   & 350 &   & 0.40 & 999.50 & \textbf{0.00} & 0.59 & 878.50 & \textbf{0.00} & 0.71 & 188.00 & \textbf{0.00} \\ 
   & 1000 &   & 0.53 & 390.00 & \textbf{0.00} & 0.80 & 341.50 & 0.13 & 0.69 & 100.00 & 0.14 \\ 
150 & 100 &   & \textbf{0.00} & 256.00 & \textbf{0.00} & \textbf{0.00} & 256.00 & \textbf{0.00} & 0.42 & 24.00 & \textbf{0.01} \\ 
    & 350 &   & 0.07 & 361.00 & \textbf{0.00} & \textbf{0.05} & 361.00 & \textbf{0.00} & 0.39 & 56.50 & \textbf{0.02} \\ 
    & 1000 &   & \textbf{0.00} & 121.00 & \textbf{0.00} & 0.13 & 119.00 & \textbf{0.01} & \textbf{0.00} & 0.00 & \textbf{0.00} \\ 
25 & 100 & Par. & 0.63 & 357.00 & \textbf{0.00} & 0.91 & 234.00 & 1.00 & 0.71 & 85.00 & 0.10 \\ 
   & 350 &   & 0.34 & 387.00 & \textbf{0.00} & 0.79 & 287.50 & 0.94 & 0.49 & 61.50 & \textbf{0.01} \\ 
   & 1000 &  & 0.43 & 384.00 & \textbf{0.00} & 0.79 & 289.50 & 0.62 & 0.71 & 65.00 & \textbf{0.01} \\ 
75 & 100 &   & 0.38 & 379.50 & \textbf{0.00} & 0.40 & 359.00 & \textbf{0.00} & 0.75 & 157.50 & 1.00 \\ 
   & 350 &   & 0.25 & 393.00 & \textbf{0.00} & 0.76 & 311.00 & 0.13 & 0.65 & 55.50 & \textbf{0.01} \\ 
   & 1000 &   & 0.15 & 393.00 & \textbf{0.00} & 0.46 & 362.00 & \textbf{0.00} & 0.46 & 58.00 & \textbf{0.01} \\ 
150 & 100 &   & 0.34 & 357.50 & \textbf{0.00} & 0.49 & 356.50 & \textbf{0.00} & 0.73 & 197.00 & 1.00 \\ 
    & 350 &   & 0.17 & 390.00 & \textbf{0.00} & 0.60 & 348.00 & \textbf{0.00} & 0.63 & 63.50 & \textbf{0.01} \\ 
    & 1000 &   & \textbf{0.00} & 400.00 & \textbf{0.00} & 0.71 & 328.50 &\textbf{0.03} & 0.34 & 24.00 & \textbf{0.00} \\ 
   \hline
\end{tabular}
\caption{Example of a result table: BC = Bhattacharyya Coefficient, W = wilcox test statistic and p = associated p-value} 
\label{LABEL}
\end{table}

>>>>

%TG: @@@ NOTE: THESE RESULTS ARE NOT FINAL - I thus didn't spend too much time describing them @@@

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Figures/RF_results_best.pdf}
\caption{\small{Effect of Character Difference on recovering the ``normal'' topology. The y axis represents the Normalised Tree Similarity using Robinson-Fould distance for matrices with 25, 75 and 150 taxa from top to bottom respectively. The x axis represents the different character difference scenarios and tree inference method with the Maximised Character Difference in Bayesian (red) and under Maximum Parsimony (orange), the Minimised Character Difference in Bayesian (dark green) and under Maximum Parsimony (light green) and the Randomised Character Difference in Bayesian (dark blue) and under Maximum Parsimony (light blue) for matrices of 100, 350 and 1000 characters in the panels from left to right.}}
\label{Fig:RF_results_best}
\end{figure}

\begin{figure}[!htbp]
\centering
   \includegraphics[width=1\textwidth]{Figures/Tr_results_best.pdf} %TG: These figures will be cleaned up once I have the final results.
\caption{Effect of Character Difference on recovering the ``normal'' topology. The axis are identical to figure \ref{Fig:RF_results_best} but y axis represents the Normalised Tree Similarity using Triplets distance.}
\label{Fig:Tr_results_best}
\end{figure}

\subsection{Effect of Character Differences on topology}

The overall amount of character difference in a matrix has an effect of the ability to recover the correct topology with maximising the character difference leading to the less loss in phylogenetic information (median $NTS_{RF}$ = 0.95 and median $NTS_{Tr}$ = 0.96) followed by simply randomising the characters (median $NTS_{RF}$ = 0.79 and median $NTS_{Tr}$ = 0.72) and minimising the character difference (median $NTS_{RF}$ = 0.6 and median $NTS_{Tr}$ = 0.28 - see supplementary material 3 for the full summary statistics).
There is a significant difference between all scenarios (maximising, minimising and randomising) with the highest probability of overlap being between maximising and randomising the character difference (Bhattacharrya coefficient of 0.89 for the $NTS_{RF}$ and 0.92 for the $NTS_{Tr}$ - Table \ref{Tab_pooledscenarios_test}) and the lowest probability between maximising and minimising the character difference (Bhattacharrya coefficient of 0.59 for the $NTS_{RF}$ and 0.63 for the $NTS_{Tr}$ - Table \ref{Tab_pooledscenarios_test})

\begin{table}[ht]
\centering
\begin{tabular}{ll|r|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & maxi:mini & 0.588 & 439466.500 & \textbf{0.000} \\ 
   & maxi:rand & 0.894 & 347624.500 & \textbf{0.000} \\ 
   & mini:rand & 0.846 & 115008.500 & \textbf{0.000} \\ 
Tr & maxi:mini & 0.628 & 443049.500 & \textbf{0.000} \\ 
   & maxi:rand & 0.921 & 348074.000 & \textbf{0.000} \\ 
   & mini:rand & 0.825 & 113171.500 & \textbf{0.000} \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled scenarios. bhatt.coeff is the Bhattacharrya Coefficient (probability of overlap), the statistic and the p.value are from a non-parametric Wilcoxon test (with Bonferonni-Holm correction), significant values are in bold.} 
\label{Tab_pooledscenarios_test}
\end{table}

\subsubsection{Effect of the number of characters}

This effect of the character difference is not dependent on the number of characters for the clade conservation (i.e. $NTS_{RF}$) for a ``similar'' number of characters (median $NTS_{RF}$ for 100, 350 and 1000 characters equals 0.76, 0.78, 0.8 respectively - see supplementary materials 3) with a significant effect only between 100 and 1000 characters (Table \ref{Tab_pooledscharacters_test}).
The number of characters affects the character difference more in terms of taxa placement for a low number of characters (median $NTS_{RF}$ for 100, 350 and 1000 characters equals 0.54, 0.70, 0.76 respectively - see supplementary materials 3) with a significant difference between 100 and 350 or 1000 characters (Table \ref{Tab_pooledscharacters_test}).
These difference have to be contrasted however by a really high probability of overlap between each number of characters and metrics (Bhattacharrya Coefficient always $>0.95$) suggesting that the significant effects of the number of characters still leads to really similar distributions.

\begin{table}[ht]
\centering
\begin{tabular}{ll|r|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & c100:c350 & \textbf{0.989} & 228495.000 & 0.174 \\ 
   & c100:c1000 & \textbf{0.983} & 218305.500 & \textbf{0.002} \\ 
   & c350:c1000 & \textbf{0.988} & 232832.500 & 0.643 \\ 
  Tr & c100:c350 & \textbf{0.965} & 203355.500 & \textbf{0.000} \\ 
   & c100:c1000 & \textbf{0.959} & 189064.000 & \textbf{0.000} \\ 
   & c350:c1000 & \textbf{0.983} & 226472.000 & 0.085 \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled number of characters. See Table \ref{Tab_pooledscenarios_test} for caption.} 
\label{Tab_pooledscharacters_test}
\end{table}

\subsubsection{Effect of the number of taxa}

Similarly than the effect of number of characters on character difference, the number of taxa seems to have only a marginal effect.
A low number of taxa (25) resulted in significant differences in both $NTS_{RF}$ and $NTS_{Tr}$ (medians for 25, 75 and 150 taxa equals 0.8, 0.76, 0.75 $NTS_{RF}$ and 0.75, 0.59 and 0.59 $NTS_{Tr}$respectively - Table \ref{Tab_pooledstaxa_test} and see supplementary materials 3).
Again, however, the significant differences have to be contrasted with still high probabilities of overlaps for each $NTS_{RF}$ and $NTS_{Tr}$ distributions for every number of taxa (Table \ref{Tab_pooledstaxa_test}).

\begin{table}[ht]
\centering
\begin{tabular}{ll|r|rr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & t25:t75 & \textbf{0.987} & 267274.500 & \textbf{0.003} \\ 
   & t25:t150 &\textbf{0.979} & 272359.500 & \textbf{0.000} \\ 
   & t75:t150 & \textbf{0.988} & 247619.500 & 1.000 \\ 
Tr & t25:t75 & \textbf{0.975} & 282017.500 & \textbf{0.000} \\ 
   & t25:t150 & \textbf{0.970} & 279730.000 & \textbf{0.000} \\ 
   & t75:t150 & \textbf{0.989} & 240414.500 & 1.000 \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled number of taxa. See Table \ref{Tab_pooledscenarios_test} for caption.} 
\label{Tab_pooledstaxa_test}
\end{table}

\subsection{Effect of Character Differences on the inference method}

Regarding the inference method, there is a significant difference in clade conservation between Bayesian and Maximum Parsimony (Table \ref{Tab_pooledsmethods_test} - median $NTS_{RF}$ of 0.82 and 0.68 respectively) but not in terms of individual taxa placements (Table \ref{Tab_pooledsmethods_test} - median $NTS_{Tr}$ of 0.72 and 0.61 respectively).

\begin{table}[ht]
\centering
\begin{tabular}{llrrr}
  \hline
metric & test & bhatt.coeff & statistic & p.value \\ 
  \hline
RF & bayesian:parsimony & 0.893 & 676940.500 & \textbf{0.000} \\ 
Tr & bayesian:parsimony & \textbf{0.982} & 547140.000 & 0.147 \\ 
   \hline
\end{tabular}
\caption{Difference between the pooled methods. See Table \ref{Tab_pooledscenarios_test} for caption.} 
\label{Tab_pooledsmethods_test}
\end{table}

\subsection{Combined effects}

When looking at the combined effect of each parameters, the maximised and minimised scenarios are always significantly different with no high probability of overlap for both $NTS_{RF}$ and $NTS_{Tr}$ (Wilcoxon rank test p.value $<0.05$ and Bhattacharrya Coefficient $<0.95$ - see supplementary material 3).
The same differences are observed when comparing the maximised scenario against the randomised one expect for: (1) the Bayesian inference with 25 taxa (with 100, 350 and 1000 characters) and with 75 taxa with 1000 characters for both $NTS_{RF}$ and $NTS_{Tr}$; and (2) the Maximum Parsimony for 25 taxa (with 350 and 1000) characters for both $NTS_{RF}$ and $NTS_{Tr}$ and 75 taxa with 100 characters for $NTS_{Tr}$.
Identically, there was always a significant difference between the minimised scenario and the randomised one was expect for the matrix of 150 taxa and 100 characters under Maximum Parsimony for $NTS_{RF}$ and the matrix of 150 and 1000 characters under Bayesian inference for $NTS_{Tr}$.
The full list of comparisons and summary statistics are available in the supplementary materials 3.
